Simulating High-Dimensional Multivariate Data

### 2021-03-01 040-monte-carlo-evaluation.Rmd
"fixed" list spacing
fixed lists by removing two spaces at end of lnes
say more about Kendall matching

In the bivariate studies, we chose arbitrary simulation parameters for three distributions, moving from the Gaussian to the discrete and non-normal, multivariate negative binomial. Under these conditions, the simulated random vectors sample the desired bivariate distribution across the entire range of pairwise correlations for the three dependency measures. The simulation results could differ for other choices of simulation settings. Specifying extreme correlations near the boundary or Frechet bounds could result in poor simulation performance. Fortunately, it is straightforward to evaluate simulation performance by using strategies similar to those completed above. We expect our random vector generation to perform well for the vast majority of NORTA-feasible correlation matrices, but advise to check the performance before making inferences/further analyses. Finally, we note that one could use our single-pass algorithm `cor_fastPD` to produce a "close" (not nearest PD) to scale to even higher dimensions with greater loss of accuracy.

>>>>

In the bivariate studies, we chose arbitrary simulation parameters for three distributions, moving from the Gaussian to the discrete and non-normal, multivariate negative binomial. Under these conditions, the simulated random vectors sample the desired bivariate distribution across the entire range of pairwise correlations for the three dependency measures. The simulation results could differ for other choices of simulation settings. Specifying extreme correlations near the boundary or Frechet bounds could result in poor simulation performance. Fortunately, it is straightforward to evaluate simulation performance by using strategies similar to those completed above. We expect our random vector generation to perform well for the vast majority of NORTA-feasible correlation matrices, but advise to check the performance before making inferences/further analyses.

Somewhat surprising, Kendall estimation and nearest PD computation scale poorly compared to Spearman and, even, approximate Pearson matching. In our experience, Kendall computation times are sensitive to the number of cores, benefiting from multi-core parallelization. This could mitigate some of the current algorithmic/implementation shortcomings. Despite this, Kendall matching is still feasible for most high-dimension data sets. Finally, we note that one could use our single-pass algorithm `cor_fastPD` to produce a "close" (not nearest PD) to scale to even higher dimensions with greater loss of accuracy.
